Pillar 1 - Sequential Pattern Mining

### 2019-03-22 Pillar 1 - Sequential Pattern Mining.Rmd
remove unused variable from df rules_clean to speed up the app
App updates

```{r rules_rules}
rules_clean <- rules_clean %>% mutate(rules_rules = rules %>% map(edit_rules))
```

```{r save rules_clean}
save(rules_clean, file = "App/rules_clean.RDATA")
```

>>>>

```{r rules_rules}
rules_clean <- rules_clean %>% mutate(rules_rules = rules %>% map(edit_rules)) %>% select(-rules)
```

```{r save rules_clean}
save(rules_clean, file = "App/rules_clean.RDATA")
save(rules_clean, file = "App/Rules/rules_clean.RDATA")
save(rules_clean, file = "App/Recommender System//rules_clean.RDATA")
```
